\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{longtable}
\usepackage{listings}

\title{Spectacle-like Window Tiling Setup on Ubuntu 24.04 (X11)}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Overview}
This guide sets up Spectacle-style window tiling on Ubuntu 24.04 using Tiling Assistant. It includes:
\begin{itemize}
    \item Installing the Extensions app
    \item Installing Tiling Assistant
    \item Disabling workspace-switching shortcuts
    \item Configuring Spectacle-like tiling shortcuts
    \item Disabling the window pop-up
\end{itemize}

\section{Install GNOME Extensions App}
Open a terminal and run:
\begin{lstlisting}[language=bash]
sudo apt update
sudo apt install gnome-extensions-app gnome-shell-extension-prefs
\end{lstlisting}
This installs the GUI app to manage GNOME extensions.

\section{Install Tiling Assistant}
\subsection*{Option A: Using Browser (Recommended)}
\begin{enumerate}
    \item Open Firefox or Chromium
    \item Go to \url{https://extensions.gnome.org/extension/3733/tiling-assistant/}
    \item Toggle the switch to ON and follow prompts to install.
\end{enumerate}

\subsection*{Option B: Using Terminal (if available in repo)}
\begin{lstlisting}[language=bash]
sudo apt install gnome-shell-extension-tiling-assistant
\end{lstlisting}

\section{Enable Tiling Assistant}
\begin{enumerate}
    \item Press \textbf{Super} (Windows key), type \textbf{Extensions}, and open the app.
    \item Find \textbf{Tiling Assistant} in the list.
    \item Flip the switch \textbf{ON} to enable it.
    \item Click the \textbf{gear icon} to open preferences.
\end{enumerate}

\section{Disable Workspace-Switching Shortcuts}
GNOME intercepts certain keys (Super + Shift + Arrow) for workspace management. Disable them:
\begin{enumerate}
    \item Open \textbf{Settings $\rightarrow$ Keyboard $\rightarrow$ Keyboard Shortcuts}.
    \item Find the \textbf{Navigation / Workspaces} section.
    \item Disable the following by clicking them and pressing Backspace:
\begin{lstlisting}
Move window to workspace left
Move window to workspace right
Move window to workspace up
Move window to workspace down
\end{lstlisting}
\end{enumerate}

\section{Configure Tiling Assistant Shortcuts}
In Tiling Assistant preferences, set the following shortcuts:

\begin{longtable}{|p{3cm}|p{5cm}|}
\hline
\textbf{Action} & \textbf{Shortcut} \\
\hline
Snap top-left & Super + Shift + Left \\
Snap top-right & Super + Shift + Right \\
Snap bottom-left & Super + Shift + Down \\
Snap bottom-right & Super + Shift + Up \\
Left half & Super + Left \\
Right half & Super + Right \\
Maximize window & Super + Up \\
Restore window & Super + Down \\
\hline
\end{longtable}

These shortcuts now work without conflicts.

\section{Disable the Tiling Pop-up (Window Overview)}
To prevent the “list of other applications” popup when tiling:
\begin{enumerate}
    \item Open \textbf{Extensions app $\rightarrow$ Tiling Assistant $\rightarrow$ Gear icon}.
    \item Look for \textbf{Window preview / popup} settings and toggle OFF.
\end{enumerate}

Alternatively, disable globally via terminal:
\begin{lstlisting}[language=bash]
gsettings set org.gnome.shell.extensions.dash-to-dock show-apps-preview false
\end{lstlisting}

\section*{Result}
\begin{itemize}
    \item Left/right tiling works (Super + Left/Right)
    \item Corner snapping works (Super + Shift + Arrow)
    \item Maximize and restore work (Super + Up/Down)
    \item No annoying pop-ups
    \item Spectacle-like window management fully functional
\end{itemize}

\section*{Optional Tips}
\begin{itemize}
    \item Dragging a window to the edge/corner also triggers tiling.
    \item Multi-monitor layouts are supported in Tiling Assistant settings.
    \item No need for gTile unless you want complex custom grids.
\end{itemize}

\end{document}